Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-11-16 paper/main.tex
Cleaned up source code

Since Tahoe-\ac{LAFS} is written in Python, we needed some way of interacting
with the C implementations of the NIST candidates. We did this by the use of
Cython, and built a python object-oriented library which we named Sha3lib.
Sha3lib supports all of the 14 second round \ac{SHA}-3 candidates, but only in
their 256-bit form.

\subsection{Sha3lib}
Sha3lib is built to mimic the functionality of
hashlib\footnote{\url{http://docs.python.org/library/hashlib.html}}, the
default python library for MD5, \ac{SHA}-1 and the \ac{SHA}-2 family. 
% TODO, figure or listing of what this means

@@

cdef class echo:
    '''
    A class that tries to mimic the behaviour of hashlib, i.e. keeping state
    so that one can update the hashing procedure instead of doing it from
    scratch.
    '''
    #cdef echo_hash_h.BitSequence *hashval
    cdef echo_hash_h.hashState previous_state
    cdef echo_hash_h.hashState state
    cdef int finished
    cdef int hashbitlen
    cdef list hashval

@@

    cpdef final(self):
        cdef echo_hash_h.BitSequence *hashval = <echo_hash_h.BitSequence *> malloc(self.hashbitlen*8)

        # We copy the state so that we can continue to update.
        # This equals hashlibs functionality, but not pycryptopp.
        self.previous_state = self.state

@@

        self.hashval = [hashval[i] for i from 0 <= i < self.hashbitlen / 8]
        free(hashval)

@@

\subsubsection{\ac{Distutils}} We use the
\ac{Distutils}\footnote{\url{http://docs.python.org/distutils/}} to build and
install our code. The alternative to doing this would be to manually transform
cython files to C-files, build the shared library from this and other relevant
C-files and then install by copying into the correct system directory where
python libraries should be stored. \ac{Distutils} also support expansion
through self defined commands, something we have utilised to do Unit Testing.
Options and configuration for \ac{Distutils} is done through a file setup.py.
Relevant configuration for compiling the echo extension can be seen in Listing.

@@

ext_modules = [
    Extension("sha3lib.hash_functions.echo.echo_hash",
        [hashpath+"echo/echo_hash.pyx", 
         hashpath+'echo/sha3nist.c', 
         hashpath+"echo/echo.c"],
    extra_compile_args=[
        '-funroll-loops',
        '-m32','-march=prescott',
        '-O2',
        '-fomit-frame-pointer']
    ),
]

setup(
    name='SHA3lib',
    version='0.1',
    description='Python bindings for SHA3-256 using Cython',
    cmdclass = {'build_ext': build_ext},
    ext_modules = ext_modules,
    packages =
        ['sha3lib',
        'sha3lib.hash_functions',
        'sha3lib.hash_functions.echo',
        ],
)

>>>>

Since Tahoe-\ac{LAFS} is written in Python, we needed some way of interacting
with the C implementations of the NIST candidates. We did this by the use of
Cython, and built a python object-oriented library which we named SHA3lib.
SHA3lib supports all of the 14 second round \ac{SHA}-3 candidates, but only in
their 256-bit form.

\subsection{SHA3lib}
SHA3lib is built to mimic the functionality of
hashlib\footnote{\url{http://docs.python.org/library/hashlib.html}}, the
default python library for MD5, \ac{SHA}-1 and the \ac{SHA}-2 family. 
% TODO, figure or listing of what this means

@@

cdef class echo:
    '''
    A class that tries to mimic the behaviour of hashlib, 
    i.e.  keeping state so that one can update the hashing 
    procedure instead of doing it from scratch.
    '''
    cdef echo_hash_h.hashState previous_state
    cdef echo_hash_h.hashState state
    cdef int finished
    cdef int hashbitlen
    cdef list hashval

@@

    cpdef final(self):
        cdef echo_hash_h.BitSequence *hashval = \
        <echo_hash_h.BitSequence *> \
        malloc(self.hashbitlen*8)

        # We copy the state so that we can continue to 
        # update. This equals hashlibs functionality, 
        # but not pycryptopp.
        self.previous_state = self.state

@@

        self.hashval = [hashval[i] for i from 0 <= i \
                        < self.hashbitlen / 8]
        free(hashval)

@@

\subsubsection{\ac{Distutils}} We use the
\ac{Distutils}\footnote{\url{http://docs.python.org/distutils/}} to build and
install our code. The alternative to doing this would be to manually transform
cython files to C-files, build the shared library from this and other relevant
C-files and then install by copying into the correct system directory where
python libraries should be stored. \ac{Distutils} also support expansion
through self defined commands, something we have utilised to do Unit Testing.
Options and configuration for \ac{Distutils} is done through a file setup.py.
Relevant configuration for compiling the echo extension, and installing SHA3lib
can bee seen in Listing \ref{lst:setup_py}.

@@

ext_modules = [
    Extension("sha3lib.hash_functions.echo.echo_hash",
        [hashpath+"echo/echo_hash.pyx", 
         hashpath+'echo/sha3nist.c', 
         hashpath+"echo/echo.c"],
    extra_compile_args=[
        '-funroll-loops',
        '-m32',
        '-march=prescott',
        '-O2',
        '-fomit-frame-pointer']
    ),
]

setup(
    name='SHA3lib',
    version='0.1',
    description='Python bindings for SHA3-256 using Cython',
    cmdclass = {'build_ext': build_ext},
    ext_modules = ext_modules,
    packages =
        ['sha3lib',
        'sha3lib.hash_functions',
        'sha3lib.hash_functions.echo',],
)
